---
title: "smallDB - A package for working with small truven databases"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview

This package contains functions for working with the small Truven database extracts.


## Examples

Load the required packages:
```{r,message=FALSE}
library(tidyverse)
library(smallDB)
```

Connect to an example database extract:
```{r}
# connect to database
con <- DBI::dbConnect(RSQLite::SQLite(), "~/Data/cftr/pancreatitis_chronic.db")
```

### Create timemap

Create a longitudinal timemap. In this example visit keys have not been added to the database,
so these will be added temporarily to create the timemap.

```{r}
tm <- build_time_map(db_con = con)

# view timemap object
tm

```

### Add diagnosis indicators

The `build_dx_indicators()` function can be used to create a list of diagnosis indicators. In this example we create a single indicator for a single diagnosis - CDI.

```{r}

# create the diagnosis list
dx_list <- list(cdi = list(icd9_codes = "00845",
                           icd10_codes = c("A047","A0471","A0472")))

# build the indicators
build_dx_indicators(db_con = con,condition_dx_list = dx_list)

```


We could also generate a list of multiple diagnoses to create multiple indicators for. Here 
I will use the `codeBuildr` package to load the diagnosis codes for AMI and CDI.
```{r, message = FALSE}
library(codeBuildr)

# load the diagnosis codes for AMI and CDI
dx_list <- load_disease_codes(c("ami","cdi"))

# view the code list
dx_list

# get the diagnosis indicators
build_dx_indicators(db_con = con,condition_dx_list = dx_list)

```
### Add medication indicators

The function `codeBuildr::load_rx_codes("all_abx")` can be used to load the ndc codes
for the group of all antibiotics.

```{r}
abx_codes <- load_rx_codes("all_abx")
```

The function `build_rx_indicators()` can then be used to collect indicators for each of the antibiotics in the `all_abx` list.

```{r}
build_rx_indicators(rx_list = abx_codes,db_con = con)
```

### Close database connection

```{r}
DBI::dbDisconnect(con)

```



